Modeling Galaxy Spectral Energy Distributions in the SDSS Spectroscopic Survey

### 2002-01-29 docs/paper/figures.tex
fix figures
git-svn-id: svn+ssh://howdy.physics.nyu.edu/usr/local/svn/kcorrect/trunk@6 75dff457-8751-0410-ab1a-cd701654ce6b
fixing stuff
git-svn-id: svn+ssh://howdy.physics.nyu.edu/usr/local/svn/kcorrect/trunk@8 75dff457-8751-0410-ab1a-cd701654ce6b

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{radec.sample8b.ps}
\caption{\label{radec.sample8b} Angular distribution, in an Aitoff
projection of equatorial coordinates, of the SDSS sample used in the
current analysis. This spectroscopic sample covers around 1,169 square
degrees and contains about 100,000 galaxy spectra.}
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{response_sdss.ps}
\caption{\label{response_sdss} Estimated filter response for all five
bands in the SDSS, as a function of rest frame wavelength for galaxies
at different redshifts. A 4 gigayear old instantaneous burst using the
models of \citet{bruzual93a} is shown for reference. {\it Top panel:}
The system consisting of \band{0.0}{u}, \band{0.0}{g}, \band{0.0}{r},
\band{0.0}{i}, and \band{0.0}{z}.  {\it Bottom panel:} The system
consisting of \band{0.0}{u}, \band{0.1}{g}, \band{0.1}{r},
\band{0.1}{i}, and \band{0.2}{z}. We use this second system rather
than the first because it requires less interpolation to determine
\band{0.1}{g}, \band{0.1}{r}, and \band{0.1}{i}, and no extrapolation to
determine \band{0.0}{u} and \band{0.1}{z}. }
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{plotaij.sample8b15.ps}
\caption{\label{plotaij.sample8b15} {\it Top panel}: Distribution of
the components of the three-parameter fit to the five-band SDSS
photometry for a random subsample consisting of 16,000 of the SDSS
galaxies. $a_0$ is linearly proportional to the flux between $3500\AA$
and $7000\AA$, while $a_1$ and $a_2$ contribute no flux in this
range. Thus, the ratios $a_1/a_0$ and $a_2/a_0$ describe the spectral
type of the galaxy. $a_2/a_0$ is the more variable parameter and thus
is the better separator of galaxy type. {\it Bottom panel}: At fixed
$a_1/a_0=-0.2$, the inferred spectra corresponding to various values
of $a_2/a_0$. Near $a_2/a_0=0.5$, the spectrum is similar to that of
an elliptical galaxy. For higher values, the spectrum becomes bluer. }
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{model.ps}
\caption{\label{model} Galaxy fluxes determined from the inferred
galaxy spectra (see Figure \ref{plotaij.sample8b15}) relative to the
observed galaxy fluxes, for all five SDSS bands, shown for a random
subsample consisting of 16,000 of the SDSS galaxies. The
residuals are shown against redshift and absolute magnitude, the two
most important systematic variables in the analysis of this paper. The
solid lines show the median values. The dashed lines show the 10\% and
90\% levels (corresponding to $1.3\sigma$ if the distribution were
Gaussian). The systematics are very small in $g$, $r$, $i$ and $z$,
but more significant in $u$. The scatter is largest in $u$ and
$z$. Nevertheless, the inferred fluxes are a good representation of
the observed fluxes.  }
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{colors.sample8b15.ps}
\caption{\label{colors.sample8b15} For galaxies in the absolute
magnitude range $-21.5<M_r<-21$, the color distribution calculated
from the inferred SEDs as a function of redshift. The left column
shows the four colors relative to \band{0.1}{r} for each galaxy versus
redshift. The right column shows the distribution of colors for
galaxies in the range $0.04<z<0.12$ {\it (dotted)} compared to the
distribution of colors of galaxies in the range $0.12<z<0.19$ {\it
(solid)}. The resulting color distribution is clearly fairly constant
with redshift.}
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{kcorrect.sample8b15.ps}
\caption{\label{kcorrect.sample8b15} $K$-corrections as a function of
redshift in all five bands for a random subsample consisting of 8,000
of the SDSS galaxies. The $K$-corrections are largest, and therefore
the most uncertain, for the \band{0.0}{u} and \band{0.1}{g} bands. The
range of $K$-corrections at each redshift reflects the range of galaxy
types at each redshift.}
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{ciCompare.sample8b15.ps}
\caption{\label{ciCompare.sample8b15} Difference in the
$K$-corrections in each band between the method used in Figure
\ref{kcorrect.sample8b15} and the method of simply interpolating
between adjacent bands fitting a power-law SED. The differences are
small in \band{0.1}{r}, \band{0.1}{i}, and \band{0.2}{z}, where galaxy
SEDs have simple shapes. There are large differences in \band{0.0}{u}
and \band{0.1}{g}, for which the 4000 \AA\ break is important. Note
particularly the systematic differences in \band{0.1}{g} with
redshift.}
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{cibreakCompare.sample8b15.ps}
\caption{\label{cibreakCompare.sample8b15} Same as Figure
\ref{ciCompare.sample8b15}, now comparing the $K$-corrections of Figure
\ref{kcorrect.sample8b15} with the ``interpolation with a break''
method. This method fits a power law between adjacent bands, except at
4000 \AA, where we fit for the size of the 4000\AA\ break (assuming
that $f(\lambda)\propto \lambda^2$ for $\lambda<4000$ \AA). This
greatly improves the agreement in \band{0.1}{g} while making the
disagreement in \band{0.0}{u} only slightly worse. These results
indicate that it important to account for the structure in the blue
region of the spectrum when performing $K$-corrections.}
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{specK.ps}
\caption{\label{specK} Similar to Figure \ref{ciCompare.sample8b15},
now comparing the $K$-corrections of Figure \ref{kcorrect.sample8b15}
with $K$-corrections determined from the spectra (which can only be
calculated for the \band{0.1}{g}, \band{0.1}{r}, and \band{0.1}{i}
bands). In all bands, the $K$-corrections are very similar, giving us
confidence in our results. This result is actually remarkable more for
what it says about the high quality of the spectrophotometry in the
SDSS survey.}
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{aperturevsz.M.sample8b15.ps}
\caption{\label{aperturevsz.M.sample8b15} }
\end{figure}

>>>>

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{response_sdss.ps}
\caption{\label{response_sdss} Estimated filter response for all five
bands in the SDSS, as a function of observed wavelength. A 4 gigayear
old instantaneous burst using the models of \citet{bruzual93a} (and
observed at $z=0$) is shown for reference.}
%at different redshifts. A 4 gigayear old instantaneous burst using the
%models of \citet{bruzual93a} is shown for reference. {\it Top panel:}
%The system consisting of \band{0.0}{u}, \band{0.0}{g}, \band{0.0}{r},
%\band{0.0}{i}, and \band{0.0}{z}.  {\it Bottom panel:} The system
%consisting of \band{0.0}{u}, \band{0.1}{g}, \band{0.1}{r},
%\band{0.1}{i}, and \band{0.2}{z}. We use this second system rather
%than the first because it requires less interpolation to determine
%\band{0.1}{g}, \band{0.1}{r}, and \band{0.1}{i}, and no extrapolation to
%determine \band{0.0}{u} and \band{0.1}{z}. 
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{k_espec_plot.ps}
\caption{\label{k_espec_plot} The four derived eigenspectra. Note that
eigenspectra \#1, \#2, and \#3 are constrained to have zero total flux in the
range between 3500\AA and 7500\AA. Eigenspectrum \#0 is not in any
sense the ``average'' spectrum. }
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{k_model_plot.ps}
\caption{\label{k_model_plot} Reconstructed galaxy fluxes relative to
the observed galaxy fluxes, for all five SDSS bands, shown for a
random subsample consisting of 16,000 of the SDSS galaxies. The
residuals are shown against redshift.  There is no systematic trend
with redshift in any band. The 5-$\sigma$ clipped estimate of the
scatter around the observed fluxes is listed for each band. In $g$,
$r$, and $i$ the scatter is consistent with the expected photometric
errors in the survey. In $z$ and $u$ there is more scatter. In the
case of $z$ this is attributable to Poisson noise in the
observations. In the case of $u$, it is not, but it may simply be that
there are more intrinic differences between galaxies in the $u$-band
than elsewhere.}
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{k_coeffdist_plot.ps}
\caption{\label{k_coeffdist_plot} {\it Top panels}: Distribution of
the components of the four-parameter fit to the five-band SDSS
photometry for a random subsample consisting of 16,000 of the SDSS
galaxies. $a_0$ is linearly proportional to the flux between $3500\AA$
and $7000\AA$, while $a_1$, $a_2$, and $a_3$ contribute no flux in
this range. Thus, the ratios $a_1/a_0$ and $a_2/a_0$ describe the
spectral type of the galaxy. $a_2/a_0$ is the most variable parameter
and thus is the better separator of galaxy type. {\it Bottom panel}:
At fixed $a_1/a_0$ and $a_2/a_0$, the inferred spectra corresponding
to various values of $a_3/a_0$. Near $a_3/a_0=-0.16$, the spectrum is
similar to that of an elliptical galaxy. For higher values, the
spectrum becomes bluer. }
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{k_coeff_plot2.ps}
\caption{\label{k_coeff_plot1} }
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{k_coeff_plot1.ps}
\caption{\label{k_coeff_plot1} }
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
%\plotone{kcorrect.sample8b15.ps}
\caption{\label{kcorrect.sample8b15} $K$-corrections as a function of
redshift in all five bands for a random subsample consisting of 8,000
of the SDSS galaxies. The $K$-corrections are largest, and therefore
the most uncertain, for the \band{0.0}{u} and \band{0.1}{g} bands. The
range of $K$-corrections at each redshift reflects the range of galaxy
types at each redshift.}
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
%\plotone{ciCompare.sample8b15.ps}
\caption{\label{ciCompare.sample8b15} Difference in the
$K$-corrections in each band between the method used in Figure
\ref{kcorrect.sample8b15} and the method of simply interpolating
between adjacent bands fitting a power-law SED. The differences are
small in \band{0.1}{r}, \band{0.1}{i}, and \band{0.2}{z}, where galaxy
SEDs have simple shapes. There are large differences in \band{0.0}{u}
and \band{0.1}{g}, for which the 4000 \AA\ break is important. Note
particularly the systematic differences in \band{0.1}{g} with
redshift.}
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
%\plotone{cibreakCompare.sample8b15.ps}
\caption{\label{cibreakCompare.sample8b15} Same as Figure
\ref{ciCompare.sample8b15}, now comparing the $K$-corrections of Figure
\ref{kcorrect.sample8b15} with the ``interpolation with a break''
method. This method fits a power law between adjacent bands, except at
4000 \AA, where we fit for the size of the 4000\AA\ break (assuming
that $f(\lambda)\propto \lambda^2$ for $\lambda<4000$ \AA). This
greatly improves the agreement in \band{0.1}{g} while making the
disagreement in \band{0.0}{u} only slightly worse. These results
indicate that it important to account for the structure in the blue
region of the spectrum when performing $K$-corrections.}
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
%\plotone{specK.ps}
\caption{\label{specK} Similar to Figure \ref{ciCompare.sample8b15},
now comparing the $K$-corrections of Figure \ref{kcorrect.sample8b15}
with $K$-corrections determined from the spectra (which can only be
calculated for the \band{0.1}{g}, \band{0.1}{r}, and \band{0.1}{i}
bands). In all bands, the $K$-corrections are very similar, giving us
confidence in our results. This result is actually remarkable more for
what it says about the high quality of the spectrophotometry in the
SDSS survey.}
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
%\plotone{aperturevsz.M.sample8b15.ps}
\caption{\label{aperturevsz.M.sample8b15} }
\end{figure}

### 2002-01-29 docs/paper/paper.tex
fixing stuff
git-svn-id: svn+ssh://howdy.physics.nyu.edu/usr/local/svn/kcorrect/trunk@8 75dff457-8751-0410-ab1a-cd701654ce6b

The resulting four templates are shown in Figure \ref{templates} in
the range $2000<\lambda<12000$\AA, the region which is constrained by
our observations. Figure \ref{coeffs} is a more illuminating
figure. It shows the pairwise joint distributions of $a_1/a_0$,
$a_2/a_0$, and $a_3/a_0$ in the top three panels. In the bottom panel,
three spectra taken from a one-dimensional sequence along the galay
locus are shown, showing that the spectra become progressively bluer
along that sequence.

>>>>

The resulting four templates are shown in Figure \ref{k_espec_plot} in
the range $2000<\lambda<12000$\AA, the region which is constrained by
our observations. Figure \ref{k_coeffdist_plot} is a more illuminating
figure. It shows the pairwise joint distributions of $a_1/a_0$,
$a_2/a_0$, and $a_3/a_0$ in the top two panels. In the bottom panel,
three spectra taken from a one-dimensional sequence along the galay
locus are shown, showing that the spectra become progressively bluer
along that sequence.
